Fast, Scalable Phrase-Based SMT Decoding

### 2016-05-06 acl.2016/acl2016.tex
changes

The search algorithm creates and destroy a large number of hypothesis and related objects. The memory allocation required puts a burden on the operating system due to the need to synchronize  memory access. This problem worsens with multi-threaded applications such as Moses.

>>>>

The search algorithm creates and destroy a large number of intermediate objects such as hypotheses and feature function states. The memory management this requires puts a burden on the operating system due to the need to synchronize memory access. This problem worsens with multi-threaded applications such as Moses.
